---
title: "Tidy data structures to support exploration <br> and modeling of temporal-context data"
subtitle: "<img src='img/tsibble.svg' height=125px>"
type: "contributed"
author: "Earo Wang"
date: "13 July, 2018 <br> slides at <http://slides.earo.me/useR18>"
output:
  xaringan::moon_reader:
    css: ["default", "remark.css"]
    self_contained: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r initial, echo = FALSE, cache = FALSE, results = 'hide'}
library(knitr)
options(htmltools.dir.version = FALSE, tibble.width = 60, tibble.print_min = 6)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.width = 12, fig.height = 11, fig.show = 'hold', 
  cache = TRUE, external = TRUE, dev = 'svglite'
)
read_chunk('R/theme.R')
```

```{r theme-remark}
```

## Tidy data

* Re-imagining data frame: `tibble`
* Spatial data: `sp`
* Text data: `tidytext`
* Google drive: `googledrive::dribble`

---

## Time series standards in R ecosystem

* **ts**
* **zoo**
* **xts**

Too many defaults as if we live in an ideal data world

---

## But the reality is ...

* Heterogeneous data types
* Implicit missing values
* Multiple measured variables
* Low time resolution

---

## The ultimate 15th time series standard

<img src='img/tsibble.svg' height=165px>

## time series + tibble = tsibble

---

## 

---

class: inverse middle center

### Joint work with Di Cook & Rob J Hyndman

### Slides created via xaringan `r emo::ji("crossed_swords")` <http://slides.earo.me/useR18>

--

### Open source <https://github.com/earowang/useR18>

--

### This work is under licensed [`r icon::fa("creative-commons")` BY-NC 4.0](https://creativecommons.org/licenses/by-nc/4.0/).
